---
title: "Collecting Viewpoints of User in Using Internet Platform Google"
author: "Jose Roland Juntanilla, Charles Daniel Songaling, Aaron John Fermano"
date: "2024-04-18"
output: html_document
---



```{r}
library(readr)
data_survey <- read.csv("Google Platform Survey.csv")
data_survey

```
# Factoring Age
```{r}
library(ggplot2)
Participants <- as.factor(data_survey$Gender)
```

```{r}

ggplot(data = data_survey, aes(x = Participants,fill=Participants)) +
  geom_bar() +
  labs(title = "Gender of Participants", x = "Gender", y = "Count") +
  scale_fill_manual(values = c("pink","violet","blue","orange"))
  theme_minimal()
```

# Plotting Age
```{r}
Participants_Age <- as.factor(data_survey$Age)
ggplot(data_survey, aes(x=Participants_Age, fill=Participants_Age)) +
  geom_bar() +
  labs(title="Age of Respondents", x="Age", y="Count") + theme_minimal()
```

#Marital Status
```{r}
data_survey$Marital.Status <- as.factor(data_survey$Marital.Status)

ggplot(data_survey, aes(x = Marital.Status, fill = Marital.Status)) +
  geom_bar() +
  labs(title = "Marital Status of Respondents", x = "Marital Status", y = "Count") +
  scale_fill_manual(values = c("orange", "red", "black","green","")) + 
  theme_minimal() + theme(plot.title = element_text(size = 8), 
        axis.title = element_text(size = 8), 
        axis.text = element_text(size = 8),  
        legend.title = element_text(size = 8), 
        legend.text = element_text(size = 8)) + 
  scale_fill_discrete(name = "Google Platforms")+ theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

#Employment Status
```{r}
data_survey$Employment.Status <- as.factor(data_survey$Employment.Status)
ggplot(data_survey, aes(x=Employment.Status, fill=Employment.Status)) +
  geom_bar() +
  labs(title="Employment Status of Respondents", x="Employment Status", y="Count") + theme_minimal() + theme(plot.title = element_text(size = 8), 
        axis.title = element_text(size = 8), 
        axis.text = element_text(size = 8),  
        legend.title = element_text(size = 8), 
        legend.text = element_text(size = 8)) + 
  scale_fill_discrete(name = "Google Platforms")+ theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

#Internet Usage per Day
```{r}
Internet_Time <- as.factor(data_survey$How.much.time.do.you.spend.on.using.the.Internet.each.day)


ggplot(data_survey, aes(x=Internet_Time, fill=Internet_Time)) +
  geom_bar() +
  labs(title="Internet Usage per Day of Respondents", x="Internet Usage per Day", y="Count") +  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

#How often do you use Google platforms?
```{r}
Usage <- as.factor(data_survey$How.often.do.you.use.Google.platforms)

ggplot(data_survey, aes(x=Usage, fill=Usage)) +
  geom_bar() +
  labs(title="How often Respondents Use Google Platforms", x="Google Platforms Usage", y="Count") + theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

#What devices do you use when using Google platforms
```{r}
Devices <- gsub(";", ",", data_survey$What.devices.do.you.use.when.using.Google.platforms)

Devices <- as.factor(data_survey$What.devices.do.you.use.when.using.Google.platforms)

ggplot(data_survey, aes(x=Devices, fill=Devices)) +
  geom_bar() +
  labs(title="Devices Used by Respondents", x="Devices Used", y="Count") + theme_minimal() + theme(plot.title = element_text(size = 8), 
        axis.title = element_text(size = 8), 
        axis.text = element_text(size = 8),  
        legend.title = element_text(size = 8), 
        legend.text = element_text(size = 8)) + 
  scale_fill_discrete(name = "Google Platforms")+ theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

#What Google platforms do you mostly use
```{r}
library(ggplot2)

Google_Platforms <- as.factor(data_survey$What.Google.platforms.do.you.mostly.use)

ggplot(data_survey, aes(x=Google_Platforms, fill=Google_Platforms)) +
  geom_bar() +
  labs(title="Google Platforms Mostly Used by Respondents", x="Google Platforms Used", y="Count") + 
  theme_minimal() +
  theme(plot.title = element_text(size = 5), 
        axis.title = element_text(size = 5), 
        axis.text = element_text(size = 5),  
        legend.title = element_text(size = 5), 
        legend.text = element_text(size = 5)) + 
  scale_fill_discrete(name = "Google Platforms")+ theme(axis.text.x = element_text(angle = 60, hjust = 1))

```

#What specific time do you usually use Google platforms on daily basis?
```{r}
Time_of_Day <- as.factor(data_survey$What.specific.time.do.you.usually.use.Google.platforms.on.daily.basis)

ggplot(data_survey, aes(x=Time_of_Day, fill=Time_of_Day)) +
  geom_bar() +
  labs(title="Time Respondents Usually Use Google platforms", x="Time", y="Count") + theme_minimal() + theme(plot.title = element_text(size = 5), 
        axis.title = element_text(size = 10), 
        axis.text = element_text(size = 10),  
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10)) + 
  scale_fill_discrete(name = "Google Platforms")+ theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

#What purposes do you use Google platforms for?
```{r}
Purposes <- as.factor(data_survey$What.purposes.do.you.use.Google.platforms.for)

ggplot(data_survey, aes(x=Purposes, fill=Purposes)) +
  geom_bar() +
  labs(title="Respondents' Purpose in Using Google Platforms", x="Purpose", y="Count") + theme_minimal() +
theme(plot.title = element_text(size = 5), 
        axis.title = element_text(size = 5), 
        axis.text = element_text(size = 5),  
        legend.title = element_text(size = 5), 
        legend.text = element_text(size = 5)) + 
  scale_fill_discrete(name = "Google Platforms")+ theme(axis.text.x = element_text(angle = 60, hjust = 1))
```
#Do you find google platform useful in your everyday life
```{r}
(Usefullness <- factor(data_survey$Do.you.find.Google.platforms.useful.in.your.everyday.life.))
Usefullness1 <- as.numeric(Usefullness)
mean(Usefullness1)
sd(Usefullness1)
```

#Does Google enable you to complete your task more Quickly
```{r}
(Task <- factor(data_survey$Does.Google.platforms.enable.you.to.accomplish.tasks.more.quickly.))
Task1 <- as.numeric(Task)
mean(Task1)
sd(Task1)
```
#Do using platforms increase your productivity
```{r}
(Productivity <- factor(data_survey$Does.using.Google.platforms.increase.your.productivity.))
Productivity1 <- as.numeric(Productivity)
mean(Productivity1)
sd(Productivity1)
```
# "By using Google platforms, do you believe it will make some aspects of life easier. For example, in academia or in your profession?  Please rate on a scale from 1 to 5
```{r}
Easier <- as.numeric(data_survey$By.using.Google.platforms..do.you.believe.it.will.make.some.aspects.of.life.easier..For.example..in.academia.or.in.your.profession...Please.rate.on.a.scale.from.1.to.5)
mean(Easier)
sd(Easier)
```
#Is your interaction with Google Platforms clear and understandable?
```{r}
Understandable <- as.numeric(data_survey$Is.your.interaction.with.Google.Platforms.clear.and.understandable.)
mean(Understandable)
sd(Understandable)
```
#Do you find it easy to become skillful at using Google platforms?
```{r}
skill <- as.numeric(data_survey$Do.you.find.it.easy.to.become.skillful.at.using.Google.platforms.)
mean(skill)
sd(skill)
```
#Do you find using Google platforms easy?
```{r}
platform <- as.numeric(data_survey$Do.you.find.using.Google.platforms.easy.)
mean(platform)
sd(platform)
```
#Did you find learning to operate Google platforms easy?
```{r}
operate <- as.numeric(data_survey$Did.you.find.learning.to.operate.Google.platforms.easy.)
mean(operate)
sd(operate)
```
#Do you think using Google platforms is a good idea or a bad idea?
```{r}
(idea <- factor(data_survey$Do.you.think.using.Google.platforms.is.a.good.idea.or.a.bad.idea.))
idea1 <- as.numeric(idea)
mean(idea1)
sd(idea1)
```
#Does Google platforms make your task/s more interesting?
```{r}
(interest <- factor(data_survey$Does.Google.platforms.make.your.task.s.more.interesting.))
interest1 <- as.numeric(interest)
mean(interest1)
sd(interest1)
```
#Did you find using Google platforms fun? 
```{r}
(fun <- factor(data_survey$Did.you.find.using.Google.platforms.fun.))
fun1 <- as.numeric(fun)
mean(fun1)
sd(fun1)
```
#Do you like using Google platforms?
```{r}
(like <- factor(data_survey$Do.you.like.using.Google.platforms.))
like1 <- as.numeric(like)
mean(like1)
sd(like1)
```
#Do people who influence your behavior think that you should use Google platforms?
```{r}
(p_influence <- factor(data_survey$Do.people.who.influence.your.behavior.think.that.you.should.use.Google.platforms.))
p_influence1 <- as.numeric(p_influence)
mean(p_influence1)
sd(p_influence1)
```
#Do people who are important to you think that you should use Google platforms?
```{r}
(p_important <- factor(data_survey$Do.people.who.are.important.to.you.think.that.you.should.use.Google.platforms.))
p_important1 <- as.numeric(p_important)
mean(p_important1)
sd(p_important1)
```
#Has the senior management of your academic or work environment been helpful in the use of Google platforms?
```{r}
(senior <- factor(data_survey$Has.the.senior.management.of.your.academic.or.work.environment.been.helpful.in.the.use.of.Google.platforms.))
senior1 <- as.numeric(senior)
mean(senior1)
sd(senior1)
```
#In general, does your academic or work environment support the use of Google platforms?
```{r}
(w_environment <- factor(data_survey$In.general..does.your.academic.or.work.environment.support.the.use.of.Google.platforms.))
w_environment1 <- as.numeric(w_environment )
mean(w_environment1)
sd(w_environment1)
```
#Do you have the necessary resources to use Google platforms?
```{r}
(resources <- factor(data_survey$Do.you.have.the.necessary.resources.to.use.Google.platforms.))
resources1 <- as.numeric(resources)
mean(resources1)
sd(resources1)
```
#Do you have the knowledge necessary to use Google platforms?
```{r}
(knowledge <- factor(data_survey$Do.you.have.the.knowledge.necessary.to.use.Google.platforms.))
knowledge1 <- as.numeric(knowledge)
mean(knowledge1)
sd(knowledge1)
```
#Do you find Google platforms not compatible with other systems you use? 
```{r}
(compatible <- factor(data_survey$Do.you.find.Google.platforms.not.compatible.with.other.systems.you.use.))
compatible1 <- as.numeric(compatible)
mean(compatible1)
sd(compatible1)
```
#Is there a specific person (or group) available for assistance if you face difficulties with Google platforms?
```{r}
(p_specific <- factor(data_survey$Is.there.a.specific.person..or.group..available.for.assistance.if.you.face.difficulties.with.Google.platforms.))
p_specific1 <- as.numeric(p_specific)
mean(p_specific1)
sd(p_specific1)
```
#Do you think you could complete a job or task using Google platforms without anyone around to guide or help you?
```{r}
(job_comp <- factor(data_survey$Do.you.think.you.could.complete.a.job.or.task.using.Google.platforms.without.anyone.around.to.guide.or.help.you.))
job_comp1 <- as.numeric(job_comp)
mean(job_comp1)
sd(job_comp1)
```
#Do you think you could complete a job or task using Google platforms if you could call for someone for help if you got stuck?
```{r}
(s_call <- factor(data_survey$Do.you.think.you.could.complete.a.job.or.task.using.Google.platforms.if.you.could.call.for.someone.for.help.if.you.got.stuck.))
s_call1 <- as.numeric(s_call)
mean(s_call1)
sd(s_call1)
```
#Do you think you could complete a job or task using Google platforms if given a lot of time to complete it?
```{r}
(lot_time <- factor(data_survey$Do.you.think.you.could.complete.a.job.or.task.using.Google.platforms.if.given.a.lot.of.time.to.complete.it.))
lot_time1 <- as.numeric(lot_time)
mean(lot_time1)
sd(lot_time1)
```
#Do you think you could complete a job or task using Google platforms if you only have the built-in help facility for assistance?
```{r}
(built_in <- factor(data_survey$Do.you.think.you.could.complete.a.job.or.task.using.Google.platforms.if.you.only.have.the.built.in.help.facility.for.assistance.))
built_in1 <- as.numeric(built_in)
mean(built_in1)
sd(built_in1)
```
#Do you feel apprehensive/uneasy about using Google platforms?
```{r}
( apprehensive <- factor(data_survey$Do.you.feel.apprehensive.uneasy.about.using.Google.platforms.))
apprehensive1 <- as.numeric( apprehensive)
mean(apprehensive1)
sd(apprehensive1)
```
#Does it scare you that you could lose information by hitting the wrong key while using Google platforms?
```{r}
( scare <- factor(data_survey$Does.it.scare.you.that.you.could.lose.information.by.hitting.the.wrong.key.while.using.Google.platforms.))
scare1 <- as.numeric( scare)
mean(scare1)
sd(scare1)
```
#How hesitant are you on using Google platforms for fear of making mistakes you cannot correct? Please rate on a scale from 1 to 5 
```{r}
hesitant <- as.numeric(data_survey$How.hesitant.are.you.on.using.Google.platforms.for.fear.of.making.mistakes.you.cannot.correct..Please.rate.on.a.scale.from.1.to.5)
mean(hesitant)
sd(hesitant)
```
#Do you find Google platforms somewhat intimidating?
```{r}
( intimidating <- factor(data_survey$Do.you.find.Google.platforms.somewhat.intimidating.))
intimidating1 <- as.numeric(intimidating)
mean(intimidating1)
sd(intimidating1)
```
#Do you intend to use Google platforms in the next months?
```{r}
( intend <- factor(data_survey$Do.you.intend.to.use.Google.platforms.in.the.next.months.))
intend1 <- as.numeric( intend)
mean(intend1)
sd(intend1)
```
#Do you predict that you would use Google platforms in the next months?
```{r}
( prediction <- factor(data_survey$Do.you.predict.that.you.would.use.Google.platforms.in.the.next.months.))
prediction1 <- as.numeric( prediction)
mean(prediction1)
sd(prediction1)
```
#Do you plan to use Google Platforms in the next months?
```{r}
( plan <- factor(data_survey$do))
plan1 <- as.numeric( plan)
mean(plan1)
sd(plan1)
```